### 2020-10-13 manuscript/manuscript.rmd
move all read.tree and read_tsv to kernel

cat_categories = read_tsv("../data_processed/tables/cat_categories.tsv")

@@

**Extended Data Table 1.** Table 1. Overview of data matrices used in this study.
```{r table_study_summary}
table_study_summary = read_tsv("../data_processed/tables/study_summary.tsv")
opts <- options(knitr.kable.NA = "")
knitr::kable(table_study_summary) %>%
  kable_styling(full_width = F)

@@

taxa_map=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Whelan2017/strict.phy")
outgroup= taxa_map %>% filter (clade_assignment=="Choanoflagellida")

tree1= read.tree("../trees_new/iqtree/Whelan2017_strict.model_test.treefile")
tree1_rooted =  root(tree1, outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree1_rooted) +
  geom_cladelabel(node=90, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=114, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=28, label="Placozoa") +
  geom_cladelabel(node=109, label="Bilateria") +
  geom_cladelabel(node=95, label="Cnidaria") +
  geom_hilight(node=90, fill="#E69F00") +
  geom_hilight(node=114, fill="#009E73") +
  geom_hilight(node=28, fill="#82D1F4") +
  geom_hilight(node=109, fill="#E6BEFF") +
  geom_hilight(node=95, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 95), hjust=-.3, size=2) + ggtitle("    WAG+C60")

tree2=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT60.con.tre")
tree2_rooted =  root(tree2, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree2_rooted) +
  geom_cladelabel(node=119, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=100, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=22, label="Placozoa") +
  geom_cladelabel(node=93, label="Bilateria") +
  geom_cladelabel(node=86, label="Cnidaria") +
  geom_hilight(node=119, fill="#E69F00") +
  geom_hilight(node=100, fill="#009E73") +
  geom_hilight(node=22, fill="#82D1F4") +
  geom_hilight(node=93, fill="#E6BEFF") +
  geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT60")

tree3=read.tree("../trees_new/sensitive/Whelan2017_strict.phy_Poisson_CAT90.con.tre")
tree3_rooted =  root(tree3, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree3_rooted) +
  geom_cladelabel(node=100, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=130, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=22, label="Placozoa") +
  geom_cladelabel(node=93, label="Bilateria") +
  geom_cladelabel(node=86, label="Cnidaria") +
  geom_hilight(node=100, fill="#E69F00") +
  geom_hilight(node=130, fill="#009E73") +
  geom_hilight(node=22, fill="#82D1F4") +
  geom_hilight(node=93, fill="#E6BEFF") +
  geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT90")
p3 = flip(p3, 100, 98)

tree4=read.tree("../trees_new/phylobayes/Whelan2017_strict.bpcomp.con.tre")
tree4_rooted =  root(tree4, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree4_rooted) +
geom_cladelabel(node=100, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=130, label="Porifera", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=22, label="Placozoa") +
geom_cladelabel(node=93, label="Bilateria") +
geom_cladelabel(node=86, label="Cnidaria") +
geom_hilight(node=100, fill="#E69F00") +
geom_hilight(node=130, fill="#009E73") +
geom_hilight(node=22, fill="#82D1F4") +
geom_hilight(node=93, fill="#E6BEFF") +
geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) <1), hjust=-.3, size=2) + ggtitle("    Poisson+CAT")
p4 = flip(p4, 100, 98)

tree5=read.tree("../trees_new/phylobayes/Whelan2017_strict.phy_GTR_CAT.con.tre")
tree5_rooted =  root(tree5, outgroup$relabelled_name, resolved.root=TRUE)
p5=ggtree(tree5_rooted) +
geom_cladelabel(node=119, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=100, label="Porifera", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=22, label="Placozoa") +
geom_cladelabel(node=93, label="Bilateria") +
geom_cladelabel(node=86, label="Cnidaria") +
geom_hilight(node=119, fill="#E69F00") +
geom_hilight(node=100, fill="#009E73") +
geom_hilight(node=22, fill="#82D1F4") +
geom_hilight(node=93, fill="#E6BEFF") +
geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1), hjust=-.3, size=2) + ggtitle("    GTR+CAT")

@@

taxa_map=read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv") %>% filter(original_matrix=="../considered_data/Philippe2009/Philippe2009.nex")
outgroup= taxa_map %>% filter (clade_assignment=="Choanoflagellida")

tree6= read.tree("../trees_new/iqtree/Philippe2009_only_choanozoa.WAG+C60.treefile")
tree6_rooted =  root(tree6, outgroup=outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree6_rooted) +
  geom_cladelabel(node=85, label="Ctenophora") +
  geom_cladelabel(node=76, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=33, label="Placozoa") +
  geom_cladelabel(node=53, label="Bilateria") +
  geom_cladelabel(node=51, label="Cnidaria") +
  geom_hilight(node=85, fill="#E69F00") +
  geom_hilight(node=76, fill="#009E73") +
  geom_hilight(node=33, fill="#82D1F4") +
  geom_hilight(node=53, fill="#E6BEFF") +
  geom_hilight(node=51, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 95), hjust=-.3, size=2) + ggtitle("    WAG+C60")

tree7=read.tree("../trees_new/sensitive/Philippe2009_only_choanozoa.phy_Poisson_CAT60.con.tre")
tree7_rooted =  root(tree7, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree7_rooted) +
  geom_cladelabel(node=83, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=32, label="Placozoa") +
  geom_cladelabel(node=58, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=83, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=32, fill="#82D1F4") +
  geom_hilight(node=58, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT60")

tree8=read.tree("../trees_new/sensitive/Philippe2009_only_choanozoa.phy_Poisson_CAT150.con.tre")
tree8_rooted =  root(tree8, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree8_rooted) +
  geom_cladelabel(node=83, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=32, label="Placozoa") +
  geom_cladelabel(node=58, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=83, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=32, fill="#82D1F4") +
  geom_hilight(node=58, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT150")

tree9=read.tree("../trees_new/phylobayes/Philippe2009_only_choanozoa.bpcomp.con.tre")
tree9_rooted =  root(tree9, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree9_rooted) +
  geom_cladelabel(node=58, label="Ctenophora") +
  geom_cladelabel(node=84, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=35, label="Placozoa") +
  geom_cladelabel(node=60, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=58, fill="#E69F00") +
  geom_hilight(node=84, fill="#009E73") +
  geom_hilight(node=35, fill="#82D1F4") +
  geom_hilight(node=60, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+CAT")

  tree10=read.tree("../trees_new/phylobayes/Philippe2009_only_choanozoa.phy_GTR_CAT.con.tre")
  tree10_rooted =  root(tree10, outgroup$relabelled_name, resolved.root=TRUE)
  p5=ggtree(tree10_rooted) +
    geom_cladelabel(node=58, label="Ctenophora") +
    geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
    geom_cladelabel(node=38, label="Placozoa") +
    geom_cladelabel(node=61, label="Bilateria") +
    geom_cladelabel(node=52, label="Cnidaria") +
    geom_hilight(node=58, fill="#E69F00") +
    geom_hilight(node=85, fill="#009E73") +
    geom_hilight(node=38, fill="#82D1F4") +
    geom_hilight(node=61, fill="#E6BEFF") +
    geom_hilight(node=52, fill="#911EB4") +
    geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    GTR+CAT")
  p5 = flip(p5, 85, 38)

@@

ribo = read_tsv("../data_processed/tables/ribosomal_gene.tsv")
busco = read_tsv("../data_processed/tables/busco_gene.tsv")

>>>>

@@

**Extended Data Table 1.** Table 1. Overview of data matrices used in this study.
```{r table_study_summary}

opts <- options(knitr.kable.NA = "")
knitr::kable(table_study_summary) %>%
  kable_styling(full_width = F)

@@

outgroup= taxa_map_whelan %>% filter (clade_assignment=="Choanoflagellida")

tree1_rooted =  root(tree1, outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree1_rooted) +
  geom_cladelabel(node=90, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=114, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=28, label="Placozoa") +
  geom_cladelabel(node=109, label="Bilateria") +
  geom_cladelabel(node=95, label="Cnidaria") +
  geom_hilight(node=90, fill="#E69F00") +
  geom_hilight(node=114, fill="#009E73") +
  geom_hilight(node=28, fill="#82D1F4") +
  geom_hilight(node=109, fill="#E6BEFF") +
  geom_hilight(node=95, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 95), hjust=-.3, size=2) + ggtitle("    WAG+C60")

tree2_rooted =  root(tree2, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree2_rooted) +
  geom_cladelabel(node=119, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=100, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=22, label="Placozoa") +
  geom_cladelabel(node=93, label="Bilateria") +
  geom_cladelabel(node=86, label="Cnidaria") +
  geom_hilight(node=119, fill="#E69F00") +
  geom_hilight(node=100, fill="#009E73") +
  geom_hilight(node=22, fill="#82D1F4") +
  geom_hilight(node=93, fill="#E6BEFF") +
  geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT60")

tree3_rooted =  root(tree3, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree3_rooted) +
  geom_cladelabel(node=100, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=130, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=22, label="Placozoa") +
  geom_cladelabel(node=93, label="Bilateria") +
  geom_cladelabel(node=86, label="Cnidaria") +
  geom_hilight(node=100, fill="#E69F00") +
  geom_hilight(node=130, fill="#009E73") +
  geom_hilight(node=22, fill="#82D1F4") +
  geom_hilight(node=93, fill="#E6BEFF") +
  geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT90")
p3 = flip(p3, 100, 98)

tree4_rooted =  root(tree4, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree4_rooted) +
geom_cladelabel(node=100, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=130, label="Porifera", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=22, label="Placozoa") +
geom_cladelabel(node=93, label="Bilateria") +
geom_cladelabel(node=86, label="Cnidaria") +
geom_hilight(node=100, fill="#E69F00") +
geom_hilight(node=130, fill="#009E73") +
geom_hilight(node=22, fill="#82D1F4") +
geom_hilight(node=93, fill="#E6BEFF") +
geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) <1), hjust=-.3, size=2) + ggtitle("    Poisson+CAT")
p4 = flip(p4, 100, 98)

tree5_rooted =  root(tree5, outgroup$relabelled_name, resolved.root=TRUE)
p5=ggtree(tree5_rooted) +
geom_cladelabel(node=119, label="Ctenophora", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=100, label="Porifera", angle=90, hjust='center', offset.text=.01) +
geom_cladelabel(node=22, label="Placozoa") +
geom_cladelabel(node=93, label="Bilateria") +
geom_cladelabel(node=86, label="Cnidaria") +
geom_hilight(node=119, fill="#E69F00") +
geom_hilight(node=100, fill="#009E73") +
geom_hilight(node=22, fill="#82D1F4") +
geom_hilight(node=93, fill="#E6BEFF") +
geom_hilight(node=86, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 1), hjust=-.3, size=2) + ggtitle("    GTR+CAT")

@@

outgroup= taxa_map_philippe %>% filter (clade_assignment=="Choanoflagellida")

tree6_rooted =  root(tree6, outgroup=outgroup$relabelled_name, resolved.root=TRUE)
p1 = ggtree(tree6_rooted) +
  geom_cladelabel(node=85, label="Ctenophora") +
  geom_cladelabel(node=76, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=33, label="Placozoa") +
  geom_cladelabel(node=53, label="Bilateria") +
  geom_cladelabel(node=51, label="Cnidaria") +
  geom_hilight(node=85, fill="#E69F00") +
  geom_hilight(node=76, fill="#009E73") +
  geom_hilight(node=33, fill="#82D1F4") +
  geom_hilight(node=53, fill="#E6BEFF") +
  geom_hilight(node=51, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 95), hjust=-.3, size=2) + ggtitle("    WAG+C60")

tree7_rooted =  root(tree7, outgroup$relabelled_name, resolved.root=TRUE)
p2= ggtree(tree7_rooted) +
  geom_cladelabel(node=83, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=32, label="Placozoa") +
  geom_cladelabel(node=58, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=83, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=32, fill="#82D1F4") +
  geom_hilight(node=58, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT60")

tree8_rooted =  root(tree8, outgroup$relabelled_name, resolved.root=TRUE)
p3=ggtree(tree8_rooted) +
  geom_cladelabel(node=83, label="Ctenophora") +
  geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=32, label="Placozoa") +
  geom_cladelabel(node=58, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=83, fill="#E69F00") +
  geom_hilight(node=85, fill="#009E73") +
  geom_hilight(node=32, fill="#82D1F4") +
  geom_hilight(node=58, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+nCAT150")

tree9_rooted =  root(tree9, outgroup$relabelled_name, resolved.root=TRUE)
p4=ggtree(tree9_rooted) +
  geom_cladelabel(node=58, label="Ctenophora") +
  geom_cladelabel(node=84, label="Porifera", angle=90, hjust='center', offset.text=.01) +
  geom_cladelabel(node=35, label="Placozoa") +
  geom_cladelabel(node=60, label="Bilateria") +
  geom_cladelabel(node=52, label="Cnidaria") +
  geom_hilight(node=58, fill="#E69F00") +
  geom_hilight(node=84, fill="#009E73") +
  geom_hilight(node=35, fill="#82D1F4") +
  geom_hilight(node=60, fill="#E6BEFF") +
  geom_hilight(node=52, fill="#911EB4") +
  geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    Poisson+CAT")

  tree10_rooted =  root(tree10, outgroup$relabelled_name, resolved.root=TRUE)
  p5=ggtree(tree10_rooted) +
    geom_cladelabel(node=58, label="Ctenophora") +
    geom_cladelabel(node=85, label="Porifera", angle=90, hjust='center', offset.text=.01) +
    geom_cladelabel(node=38, label="Placozoa") +
    geom_cladelabel(node=61, label="Bilateria") +
    geom_cladelabel(node=52, label="Cnidaria") +
    geom_hilight(node=58, fill="#E69F00") +
    geom_hilight(node=85, fill="#009E73") +
    geom_hilight(node=38, fill="#82D1F4") +
    geom_hilight(node=61, fill="#E6BEFF") +
    geom_hilight(node=52, fill="#911EB4") +
    geom_text2(aes(label=label, subset = !is.na(as.numeric(label)) & as.numeric(label) < 0.95), hjust=-.3, size=2) + ggtitle("    GTR+CAT")
  p5 = flip(p5, 85, 38)

@@
